An HPSG account for verbal reduplication in Mandarin Chinese

### 2023-06-03 chapters/ch05-Analysis.tex
Update 2023-06-03-19:08:01

In what follows, we suggest a new lexical-rule-based analysis of aspect marking and reduplication
using MRS, as proposed in \citet{LuMueller2021}.

The implicational constraint in  (\ref{avm:redup}) shows the constraints on all structures of type
\textit{verbal-reduplication-lr} for Mandarin Chinese. 
Such structures take a verb as \textsc{lexical-daughter (lex-dtr)}.  
The output reduplicates the \textsc{phonology (phon)} of the input verb with the possibility to have further phonological material in between.
\etag{} indicates an underspecified list which could be empty or not. 
A delimitative relation is appended to the \textsc{rels} value of the input verb, 
and it takes the event index of the input verb as argument. 
The label of the output \iboxb{2} is identified with the label of the input and with the label of the delimitative relation, 
hence \type{delimitative-rel} is treated as a modifier.
 Further relations can be added at the beginning of the \textsc{relations (rels)} list to allow for
the additional perfective meaning in A-\textit{le}-A and A-\textit{le}-\textit{yi}-A. 
The combination with the perfective will be elaborated on in the following paragraphs.

\ea
\type{verbal-reduplication-lr} \impl\\
\scalebox{.9}{%
    \avm{
        [
        phon & \1 $\oplus$ \etag $\oplus$ \1\\
        synsem & [ loc\textbar cont [ ltop & \2 \\
        ind  & \3 ] ]\\
        rels & \etag $\oplus$ \4 $\oplus$ < [\type*{delimitative-rel}\\
        lbl & \2\\
        arg0 & \3 ] > \smallskip\\
        lex-dtr & [phon \1\\
        synsem\textbar loc & [cat  & [ head & verb ] \\
        cont & [ ltop & \2\\
        ind  & \3 ]]\\
        rels \4 ] ]
}}
\label{avm:redup}
\z

To account for the variations in the phonology of the reduplication as well as 
the combination with the phonology and semantics of the perfective aspect marker \textit{le}, 
the type hierarchy of lexical rules in \figref{fig:typehi} is put forward. 
\begin{figure}
    \centering
    \scalebox{.9}{\begin{forest}
        type hierarchy
        [,phantom
        [,phantom
        [verbal-reduplication-lr,name=verbal-reduplicaiton-lr
        [non-perfective-reduplicaiton-lr
        [a-a-lr]
        [a-yi-a-lr]]
        [,identify=!r211]]]
        [aspect-marking-lr
        [perfective-lr
        [perfective-reduplicaiton-lr%,edge to=verbal-reduplicaiton-lr
        [a-le-yi-a-lr]
        [a-le-a-lr]]
        [v-le-lr]]
        [durative-lr]
        [\ldots]]]
    \end{forest}
}
    \caption{Type hierarchy for lexical rules of verbal reduplication and \textit{le}}
    \label{fig:typehi}
\end{figure}
Apart from the type \type{perfective-reduplication-lr}, 
which adds the inherited perfective relation, 
there is a subtype \type{non-perfective-reduplication-lr}, 
which does not add further relations. 
Hence, what is \etag in the \textsc{rels} list in (\ref{avm:redup}) is the empty list in (\ref{avm:nonperf}):
\ea\label{avm:nonperf}
\type{non-perfective-verbal-reduplication-lr} \impl\\
\scalebox{.9}{%
    \avm{
        [
        rels & \1 $\oplus$ < [ ] > \smallskip\\
        lex-dtr & [ rels \1 ] ]
    }
}
\z
The \textsc{rels} list of the output of the lexical rule \iboxb{1} is the \textsc{rels} list of
the daughter plus one element. 
Since the element is specified in the supertype, it has not been specified in (\ref{avm:nonperf}) again.

\type{non-perfective-verbal-reduplication-lr} has \type{aa-lr} and \type{a-yi-a-lr} as direct subtypes.
(\ref{avm:AA}) and (\ref{avm:AyiA}) show \type{aa-lr} and \type{a-yi-a-lr}, respectively.
As subtypes of \type{ver\-bal\hyp{}re\-dup\-li\-ca\-tion\hyp{}lr} illustrated in (\ref{avm:redup}), 
both inherit the constraints on the \textsc{lex-dtr} and on the semantics of the output, 
and because of (\ref{avm:nonperf}), no extra material is appended to the \textsc{rels} value of the input verb
and the list containing the \type{delimitative-rel}.
 In addition to the inherited constraints,
\type{aa-lr} and \type{a-yi-a-lr} specify the phonology of the output differently.
\type{aa-lr} determines that the \etag between the two phonological copies in (\ref{avm:redup}) is empty, 
whereas \type{a-yi-a-lr} specifies this list of phonological material as \phonliste{ yi }:

\ea\label{avm:constr-AA}
Constraints on lexical rules of type \type{aa-lr} and \type{a-yi-a-lr}:
%\begin{tabular}{@{}l@{\hspace{2cm}}l@{}}
 \ea   \type{aa-lr} \impl \\%& 
    \scalebox{.9}{%
        \avm{
            [phon & \1 $\oplus$ \1\\
            lex-dtr & [phon & \1] ]
    }} %& 
\ex	\type{a-yi-a-lr} \impl\\
     \scalebox{.9}{%
        \avm{
            [phon & \1 $\oplus$ \phonliste{ yi } $\oplus$ \1\\
            lex-dtr & [phon & \1] ]
    }}
%\end{tabular}
\z
\z

@@

\ea\label{avm:AA}
The AA lexical rule with all constraints inherited from the supertypes:
\scalebox{.9}{%
    \avm{
        [\type*{aa-lr}\\
        phon & \1 $\oplus$ \1\\
        synsem & [ loc\textbar cont [ ltop & \2 \\
        ind  & \3 ] ]\\
        rels & \4 $\oplus$ < [\type*{delimitative-rel}\\
        lbl & \2\\
        arg0 & \3 ] >\\
        lex-dtr & [phon & \1\\
        \punk{synsem\textbar loc}{[cat  & [ head & verb ]\\
            cont & [ ltop & \2\\
            ind  & \3 ]]}\\
        rels & \4]
        ]
}}
\z

\ea\label{avm:AyiA}
The A-\textit{yi}-A lexical rule with all constraints inherited from the supertypes:
\scalebox{.9}{%
    \avm{
        [\type*{a-yi-a-lr}\\
        phon & \1  $\oplus$ \phonliste{ yi } $\oplus$ \1\\
        synsem & [ loc\textbar cont [ ltop & \2 \\
        ind  & \3 ] ]\\
        rels &  \4 $\oplus$ < [\type*{delimitative-rel}\\
        lbl & \2\\
        arg0 & \3 ] >\\
        lex-dtr & [phon & \1\\
        \punk{synsem\textbar loc}{[cat  & [ head & verb ]\\
            cont & [ ltop & \2\\
            ind  & \3 ]]}\\
        rels & \4]
        ]
}}
\z

@@

\ea\label{avm:pfv-old}
Perfective lexical rule adapted from \citet[246]{MuellerLipenkova2013}:\\
\scalebox{.9}{%
    \avm{
        [\type*{perfective-lr}\\
        phon & \1 \+ \phonliste{ le }\\
        \punk{synsem\textbar cont}{ [ ltop & \2\\
            ind & \3 ]}\\ 
        rels & <[\type*{perfective-rel}\\
        lbl  & \2\\
        arg0 & \3\\
        arg1 & \4]> \+ \5\smallskip\\
        lex-dtr & [phon & \1\\
        \punk{synsem\textbar loc}{[cat & [ head & verb]\\
            cont & [ ltop & \4\\
            ind & \3]]}\\
        rels & \5]
        ]
}}
\z
The event variables \iboxb{3} of the input and the output verb are shared. 
The \textsc{ltop} of the output of the lexical rule \iboxb{2} is the label of the perfective relation, 
and this relation scopes over the embedded verb. 
The handle of the embedded verb \iboxb{4} is the argument of the \type{perfective-rel}.

@@

\ea\label{avm:pfv-new}
Type constraints on the type \type{perfective-lr} from which other subtypes inherit:\\
\scalebox{.9}{%
    \avm{
        [\type*{perfective-lr}\\
        phon & \etag $\oplus$ \phonliste{ le } $\oplus$ \etag\\
        \punk{synsem\textbar cont}{ [ltop & \2\\
            ind  & \3]}\\ 
        rels & <[\type*{perfective-rel}\\
        lbl  & \2\\
        arg0 & \3\\
        arg1 & \4 ]> $\oplus$ \5 $\oplus$ \etag\smallskip\\
        lex-dtr & [%phon & \1\\
        \punk{synsem\textbar loc}{[cat & [ head & verb ]\\
            cont & [ ltop & \4\\
            ind  & \3]]}\\
        rels & \5]
        ]
}}
\z

\type{v-le-lr} as given in (\ref{avm:vle}) inherits from \type{perfective-lr} and specifies that the first element in the output \textsc{phon} list is identified with the \textsc{phon} value of the input verb
and that nothing else comes after \phonliste{ le }.
Furthermore, no other list can be appended at the end of the \textsc{rels} list of the output anymore.
This corresponds to the proposal of \citet[246]{MuellerLipenkova2013} shown in (\ref{avm:pfv-old}), 
which accounts for the simple perfective marking of verbs.

\ea\label{avm:vle}
Structure of type \type{v-le-lr} with constraints inherited from \type{perfective-lr}:\\
\scalebox{.9}{%
    \avm{
        [\type*{v-le-lr}\\
        phon & \1 $\oplus$ \phonliste{ le }\\
        \punk{synsem\textbar cont\textbar ltop}{ \2}\\ 
        rels & <[\type*{perfective-rel}\\
        lbl  & \2\\
        arg0 & \3\\
        arg1 & \4]> $\oplus$ \5\smallskip\\
        lex-dtr & [phon & \1\\
        cat  & [ head & verb\\
        cont & [ltop & \4\\
        ind & \3]]\\
        rels & \5]]
}}
\z

@@

\ea\label{avm:pfv-redup}
Perfective and reduplication combined: type \type{perfective-reduplication-lr} with
constraints inherited from \type{perfective-lr} and \type{verbal-reduplication-lr}:
%\resizebox{\linewidth}{!}{
    \scalebox{.9}{%
        \avm{
            [\type*{perfective-reduplication-lr}\\
            phon & \1 $\oplus$ \phonliste{ le } $\oplus$ \etag $\oplus$ \1\\
            \punk{synsem\textbar cont\textbar ltop}{ \2}\\ 
            rels & <[\type*{perfective-rel}\\
            lbl & \2\\
            arg0 & \3\\
            arg1 & \4]>
            $\oplus$ \5 $\oplus$
            <[\type*{delimitative-rel}\\
            lbl  & \4\\
            arg0 & \3]>\\
            lex-dtr & [phon & \1\\
            synsem\textbar loc & [cat  & [ head & verb ]\\
            cont & [ ltop & \4\\
            ind  & \3]]\\
            rels & \5]
            ]
    }}
    %}
\z
For example (\ref{ex-he-tasted-the-soup-a-little-bit}), repeated here as (\ref{ex-he-tasted-the-soup-a-little-bit2}), we get the  MRS representation in (\ref{ex:mrs-soup}),
where h1 and h2 correspond to the handles \ibox{2} and \ibox{4} and e1 to the event variable \ibox{3}:
\ea\label{ex-he-tasted-the-soup-a-little-bit2}
    \gll ta \textit{chang}-\textit{le}-\textit{chang} tang.\\
    he taste-\textsc{pfv}-taste soup\\
    \glt `He tasted the soup a little bit.'
 \z
\ea\label{ex:mrs-soup}
h1 \sliste{ h1:perfective(e1,h2), h2:taste(e1,he,soup), h2:delimitative(e1) }
\z
So the delimitative relation is treated as an adjunct to the main relation of the verb, 
and the perfective relation scopes over both the main relation and the delimitative relation.

@@

\ea\label{avm:AleA}
%\begin{tabular}{@{}l@{\hspace{2cm}}l@{}}
\ea    \scalebox{.9}{%
        \avm{
            [\type*{a-le-yi-a-lr}\\
            phon & \1 \+ \phonliste{ le, yi } \+ \1\\
            lex-dtr & [phon & \1
            ]
            ]
    }}%&
\ex    \scalebox{.9}{%
        \avm{
            [\type*{a-le-a-lr}\\
            phon & \1 \+ \phonliste{ le } \+ \1\\
            lex-dtr & [phon & \1
            ]
            ]
    }}
%\end{tabular}
\z
\z

Since the above-described lexical rules do not constrain the number of syllables of the input verb, but simply reduplicate its phonology  as a whole,
they can also account for the ABAB and the AB-\textit{le}-AB forms of reduplication,
as long as the input verb is disyllabic.
Notice that  the lexical rules above also produce AB-\textit{yi}-AB and AB\hyp{}\textit{le}\hyp{}\textit{yi}\hyp{}AB for disyllabic input verbs.
Although these forms are generally considered unacceptable \citetext{\citealp[160]{BascianoMelloni2017}, \citealp[275--276]{Hong1999}, \citealp[30]{LiThompson1981}, \citealp[239]{YangWei2017}}, 
\citet[269]{Fan1964} and \citet[143]{Sui2018} considered AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB to be possible, even though they both recognized that these two forms are rare.
Indeed, a few examples of AB\hyp{}\emph{yi}\hyp{}AB and AB\hyp{}\emph{le}\hyp{}\emph{yi}\hyp{}AB in Early Mandarin (12th to 20th centuries) (\ref{ex:AByiAB-lu})--(\ref{ex:AByiAB-pu}) and Modern Mandarin (\ref{ex:AByiAB-rou1})--(\ref{ex:ABleyiAB-ccl}) were found.

\footnotetext[17]{\textit{Yuanqu xuan: Luzhailang [Selected Yuanqu: Luzhailang]}, as cited in \citet[15]{Zhang2000}}
\footnotetext[18]{\textit{Yuan Ming juan: Piaotongshi [Yuan and Ming volume: Piaotongshi]}, 308, as cited in \citet[15]{Zhang2000}}
\footnotetext[19]{Rou, Shi. 1975. \textit{Roushi xiaoshuo xuanji [Selected novels of Roushi]}, 31. Beijing: People's Literature Publishing House.}
\footnotetext[20]{Li, Jieren. 1962. \textit{Da bo [Great wave]}, 3rd band, 171. Beijing: The Writers Publishing House.}
\ea\label{ex:ABleyiAB}
\ea\label{ex:AByiAB-lu}
\gll ni yu wo \textit{zhengli-yi-zhengli}.\footnotemark\\
you let me arrange-one-arrange\\
\glt `Let me arrange it a little bit!''

\ex\label{ex:AByiAB-pu}
\gll ni \textit{dating-yi-dating}.\footnotemark\\
you inquire-one-inquire\\
\glt `Inquire about it a little bit!''

@@

\ex\label{ex:ABleyiAB-ccl}
\gll jiduo sanluan-zhe de chuan li de dengguang, ye huyinhumie de \textit{bianhuan-le-yi-bianhuan} weizhi.\\
many scattered-\textsc{dur} \textsc{de} boat in \textsc{de} light also flicker \textsc{de} change-\textsc{pfv}-one-chang position\\ \jambox{(CCL)}
\glt `Many scattered lights in the boats also changed their positions a little bit, flickering.'
\z
\z

@@

\ea\label{ex:AyiAkan}
\ea
\gll teyi gongneng de yanjiuzhe-men bufang ruci \textit{shi-yi-shi-kan} \ldots\\
special power \textsc{de} researcher-\textsc{pl} may.as.well such try-one-try-look\\ \jambox{(CCL)}
\glt `Researchers of special power may as well have a try as such as see \ldots'

\ex 
\gll danshi dui fa mei fa-guo hege-zheng, yijing shuo bu qing le, xuyao \textit{cha-yi-cha-kan}.\\
but about issue not issue-\textsc{exp} conformity-certificate already say not clealy \textsc{ptc} need check-one-chek-look\\ \jambox{(CCL)}
\glt `But one already cannot say it clearly anymore, whether a certificate of conformity is issued or not. One needs to have a check and see.'

\ex
\gll rang wo lai \textit{cai-yi-cai-kan}.\\
let I come guess-one-guess-look\\ \jambox{({CCL})}
\glt `Let me have a guess.'

\ex
\gll da-laoban-men yao \textit{deng-yi-deng-kan}\\
big-boss-\textsc{pl} need wait-one-wait-look\\ \jambox{(CCL)}
\glt `Big bosses need to wait a little bit and see.'

\ex
\gll furen ni dao \textit{shu-yi-shu-kan}, zhe zhu hua de huaduo gong you ji zhong yanse.\\
madam you just count-one-count-look this \textsc{clf} flower \textsc{de} blossom in.total have how.many \textsc{clf} color\\ \jambox{(CCL)}
\glt `Madam, just try to count and see how many colors the blossom of this flower has in total.'
\z
\z
Due to the prominent tentative, trying meaning of AA-\textit{kan} and A-\textit{kan}-\textit{kan}, they are not compatible with the perfective aspect marker \textit{le} semantically,
as one usually cannot try something that is already realized.
Thus, structures such as  A\hyp{}\textit{le}\hyp{}A\hyp{}\textit{kan} and A\hyp{}\textit{kan\hyp{}le\hyp{}kan} are considered pragmatically infelicitous.

>>>>

In what follows, we suggest a new lexical-rule-based analysis of aspect marking and reduplication
using Minimal Recursion Semantics (MRS; \citealt{Copestakeetal2005}).%, as proposed in \citet{LuMueller2021}.

The implicational constraint in  (\ref{avm:redup}) shows the constraints on all structures of type
\textit{verbal-reduplication-lr} for Mandarin Chinese. 
Such structures take a verb as \textsc{lexical-daughter (lex-dtr)}.  
The output reduplicates the \textsc{phonology (phon)} of the input verb with the possibility to have further phonological material in between.
\etag{} indicates an underspecified list which could be empty or not. 
A delimitative relation is appended to the \textsc{relations (rels)} value of the input verb, 
and it takes the event index of the input verb as argument. 
The label of the output \iboxb{2} is identified with the label of the input and with the label of the delimitative relation, 
hence \type{delimitative-rel} is treated as a modifier.
 Further relations can be added at the beginning of the \textsc{rels} list to allow for
the additional perfective meaning in A-\textit{le}-A and A-\textit{le}-\textit{yi}-A. 
The combination with the perfective will be elaborated on in the following paragraphs.

\ea
\type{verbal-reduplication-lr} \impl\\
%\scalebox{.9}{%
    \avm{
        [
        phon & \1 $\oplus$ \etag $\oplus$ \1\\
        synsem & [ loc\textbar cont [ ltop & \2 \\
        ind  & \3 ] ]\\
        rels & \etag $\oplus$ \4 $\oplus$ < [\type*{delimitative-rel}\\
        lbl & \2\\
        arg0 & \3 ] > \smallskip\\
        lex-dtr & [phon \1\\
        synsem\textbar loc & [cat  & [ head & verb ] \\
        cont & [ ltop & \2\\
        ind  & \3 ]]\\
        rels \4 ] ]
}
%}
\label{avm:redup}
\z

To account for the variations in the phonology of the reduplication as well as 
the combination with the phonology and semantics of the perfective aspect marker \textit{le}, 
the type hierarchy of lexical rules in \figref{fig:typehi} is put forward. 
\begin{figure}
    \centering
    \scalebox{.9}{\begin{forest}
        type hierarchy
        [,phantom
        [,phantom
        [verbal-reduplication-lr,name=verbal-reduplicaiton-lr
        [non-perfective-reduplicaiton-lr
        [a-a-lr]
        [a-yi-a-lr]]
        [,identify=!r211]]]
        [aspect-marking-lr
        [perfective-lr
        [perfective-reduplicaiton-lr%,edge to=verbal-reduplicaiton-lr
        [a-le-yi-a-lr]
        [a-le-a-lr]]
        [v-le-lr]]
        [durative-lr]
        [\ldots]]]
    \end{forest}
}
    \caption{Type hierarchy for lexical rules of verbal reduplication and \textit{le}}
    \label{fig:typehi}
\end{figure}
Apart from the type \type{perfective-reduplication-lr}, 
which adds the inherited perfective relation, 
there is a subtype \type{non-perfective-reduplication-lr}, 
which does not add further relations. 
Hence, what is \etag in the \textsc{rels} list in (\ref{avm:redup}) is the empty list in (\ref{avm:nonperf}):
\ea\label{avm:nonperf}
\type{non-perfective-verbal-reduplication-lr} \impl\\
%\scalebox{.9}{%
    \avm{
        [
        rels & \1 $\oplus$ < [ ] > \smallskip\\
        lex-dtr & [ rels \1 ] ]
    }
%}
\z
The \textsc{rels} list of the output of the lexical rule is the \textsc{rels} list of
the daughter \iboxb{1} plus a list with one element. 
Since this element is specified in the supertype, it is not specified in (\ref{avm:nonperf}) again.

\type{non-perfective-verbal-reduplication-lr} has \type{aa-lr} and \type{a-yi-a-lr} as direct subtypes.
(\ref{avm:AA}) and (\ref{avm:AyiA}) show \type{aa-lr} and \type{a-yi-a-lr}, respectively.
As subtypes of \type{ver\-bal\hyp{}re\-dup\-li\-ca\-tion\hyp{}lr} illustrated in (\ref{avm:redup}), 
both inherit the constraints on the \textsc{lex-dtr} and on the semantics of the output, 
and because of (\ref{avm:nonperf}), no extra material is appended to the \textsc{rels} value of the input verb
and the list containing the \type{delimitative-rel}.
 In addition to the inherited constraints,
\type{aa-lr} and \type{a-yi-a-lr} specify the phonology of the output differently.
\type{aa-lr} determines that the \etag between the two phonological copies in (\ref{avm:redup}) is the empty list, 
whereas \type{a-yi-a-lr} specifies this list of phonological material as \phonliste{ yi }:

\ea\label{avm:constr-AA}
Constraints on lexical rules of type \type{aa-lr} and \type{a-yi-a-lr}:
%\begin{tabular}{@{}l@{\hspace{2cm}}l@{}}
 \ea   \type{aa-lr} \impl \\%& 
  %  \scalebox{.9}{%
        \avm{
            [phon & \1 $\oplus$ \1\\
            lex-dtr & [phon & \1] ]
    }
%} %& 
\ex	\type{a-yi-a-lr} \impl\\
 %    \scalebox{.9}{%
        \avm{
            [phon & \1 $\oplus$ \phonliste{ yi } $\oplus$ \1\\
            lex-dtr & [phon & \1] ]
    }
%}
%\end{tabular}
\z
\z

@@

\ea\label{avm:AA}
The AA lexical rule with all constraints inherited from the supertypes:
%\scalebox{.9}{%
    \avm{
        [\type*{aa-lr}\\
        phon & \1 $\oplus$ \1\\
        synsem & [ loc\textbar cont [ ltop & \2 \\
        ind  & \3 ] ]\\
        rels & \4 $\oplus$ < [\type*{delimitative-rel}\\
        lbl & \2\\
        arg0 & \3 ] >\\
        lex-dtr & [phon & \1\\
        \punk{synsem\textbar loc}{[cat  & [ head & verb ]\\
            cont & [ ltop & \2\\
            ind  & \3 ]]}\\
        rels & \4]
        ]
}
%}
\z

\ea\label{avm:AyiA}
The A-\textit{yi}-A lexical rule with all constraints inherited from the supertypes:
%\scalebox{.9}{%
    \avm{
        [\type*{a-yi-a-lr}\\
        phon & \1  $\oplus$ \phonliste{ yi } $\oplus$ \1\\
        synsem & [ loc\textbar cont [ ltop & \2 \\
        ind  & \3 ] ]\\
        rels &  \4 $\oplus$ < [\type*{delimitative-rel}\\
        lbl & \2\\
        arg0 & \3 ] >\\
        lex-dtr & [phon & \1\\
        \punk{synsem\textbar loc}{[cat  & [ head & verb ]\\
            cont & [ ltop & \2\\
            ind  & \3 ]]}\\
        rels & \4]
        ]
}
%}
\z

@@

\ea\label{avm:pfv-old}
Perfective lexical rule adapted from \citet[246]{MuellerLipenkova2013}:\\
%\scalebox{.9}{%
    \avm{
        [\type*{perfective-lr}\\
        phon & \1 \+ \phonliste{ le }\\
        \punk{synsem\textbar loc\textbar cont}{ [ ltop & \2\\
            ind & \3 ]}\\ 
        rels & <[\type*{perfective-rel}\\
        lbl  & \2\\
        arg0 & \3\\
        arg1 & \4]> \,\+\, \5\smallskip\\
        lex-dtr & [phon & \1\\
        \punk{synsem\textbar loc}{[cat & [ head & verb]\\
            cont & [ ltop & \4\\
            ind & \3]]}\\
        rels & \5]
        ]
}
%}
\z
The event variables \iboxb{3} of the input and the output verb are shared. 
The \textsc{ltop} of the output of the lexical rule \iboxb{2} is the label of the perfective relation, 
and this relation scopes over the embedded verb. 
The handle of the embedded verb \iboxb{4} is the argument of the \type{perfective-rel}.

@@

\ea\label{avm:pfv-new}
Type constraints on the type \type{perfective-lr} from which other subtypes inherit:\\
%\scalebox{.9}{%
    \avm{
        [\type*{perfective-lr}\\
        phon & \etag $\oplus$ \phonliste{ le } $\oplus$ \etag\\
        \punk{synsem\textbar loc \textbar cont}{ [ltop & \2\\
            ind  & \3]}\\ 
        rels & <[\type*{perfective-rel}\\
        lbl  & \2\\
        arg0 & \3\\
        arg1 & \4 ]> $\oplus$ \5 $\oplus$ \etag\smallskip\\
        lex-dtr & [%phon & \1\\
        \punk{synsem\textbar loc}{[cat & [ head & verb ]\\
            cont & [ ltop & \4\\
            ind  & \3]]}\\
        rels & \5]
        ]
}
%}
\z

\type{v-le-lr} with all inherited constraints as given in (\ref{avm:vle}) inherits from \type{perfective-lr} and specifies that the first element in the output \textsc{phon} list is identified with the \textsc{phon} value of the input verb
and that nothing else comes after \phonliste{ le }.
Furthermore, no other list can be appended at the end of the \textsc{rels} list of the output anymore.
This corresponds to the proposal of \citet[246]{MuellerLipenkova2013} shown in (\ref{avm:pfv-old}), 
which accounts for the simple perfective marking of verbs.

\ea\label{avm:vle}
Structure of type \type{v-le-lr} with constraints inherited from \type{perfective-lr}:\\
%\scalebox{.9}{%
    \avm{
        [\type*{v-le-lr}\\
        phon & \1 $\oplus$ \phonliste{ le }\\
        \punk{synsem\textbar loc \textbar cont\textbar ltop}{ \2}\\ 
        rels & <[\type*{perfective-rel}\\
        lbl  & \2\\
        arg0 & \3\\
        arg1 & \4]> $\oplus$ \5\smallskip\\
        lex-dtr & [phon & \1\\
        synsem\textbar loc \textbar cat  & [ head & verb\\
        cont & [ltop & \4\\
        ind & \3]]\\
        rels & \5]]
}
%}
\z

@@

\ea\label{avm:pfv-redup}
Perfective and reduplication combined: type \type{perfective-reduplication-lr} with
constraints inherited from \type{perfective-lr} and \type{verbal-reduplication-lr}:
%\resizebox{\linewidth}{!}{
 %   \scalebox{.9}{%
        \avm{
            [\type*{perfective-reduplication-lr}\\
            phon & \1 $\oplus$ \phonliste{ le } $\oplus$ \etag $\oplus$ \1\\
            \punk{synsem\textbar loc \textbar cont\textbar ltop}{ \2}\\ 
            rels & <[\type*{perfective-rel}\\
            lbl & \2\\
            arg0 & \3\\
            arg1 & \4]>
            $\oplus$ \5 $\oplus$
            <[\type*{delimitative-rel}\\
            lbl  & \4\\
            arg0 & \3]>\\
            lex-dtr & [phon & \1\\
            synsem\textbar loc & [cat  & [ head & verb ]\\
            cont & [ ltop & \4\\
            ind  & \3]]\\
            rels & \5]
            ]
    }
%}
    %}
\z
For example (\ref{ex-he-tasted-the-soup-a-little-bit}), repeated here as (\ref{ex-he-tasted-the-soup-a-little-bit2}), we get the  MRS representation in (\ref{ex:mrs-soup}),
where h1 and h2 correspond to the handles \ibox{2} and \ibox{4} and e1 to the event variable \ibox{3}:
\ea\label{ex-he-tasted-the-soup-a-little-bit2}
    \gll ta \textit{chang}-\textit{le}-\textit{chang} tang.\\
    he taste-\textsc{pfv}-taste soup\\
    \glt `He tasted the soup a little bit.'
 \z
\ea\label{ex:mrs-soup}
h1 \sliste{ h1:perfective(e1,h2), h2:taste(e1,he,soup), h2:delimitative(e1) }
\z
So the delimitative relation is treated as an adjunct to the main relation of the verb, 
and the perfective relation scopes over both the main relation and the delimitative relation.

@@

\ea\label{avm:AleA}
%\begin{tabular}{@{}l@{\hspace{2cm}}l@{}}
\ea    %\scalebox{.9}{%
        \type{a-le-yi-a-lr} \impl\\
        \avm{
            [%\type*{a-le-yi-a-lr}\\
            phon & \1 \+ \phonliste{ le, yi } \+ \1\\
            lex-dtr & [phon & \1
            ]
            ]
    }
%}%&
\ex   % \scalebox{.9}{%
    \type{a-le-a-lr} \impl\\
        \avm{
            [%\type*{a-le-a-lr}\\
            phon & \1 \+ \phonliste{ le } \+ \1\\
            lex-dtr & [phon & \1
            ]
            ]
    }
%}
%\end{tabular}
\z
\z

Since the above-described lexical rules do not constrain the number of syllables of the input verb, but simply reduplicate its phonology  as a whole,
they can also account for the ABAB and the AB-\textit{le}-AB forms of reduplication,
as long as the input verb is disyllabic.
Notice that  the lexical rules above also produce AB-\textit{yi}-AB and AB\hyp{}\textit{le}\hyp{}\textit{yi}\hyp{}AB for disyllabic input verbs.
Although these forms are generally considered unacceptable \citetext{\citealp[160]{BascianoMelloni2017}, \citealp[275--276]{Hong1999}, \citealp[30]{LiThompson1981}, \citealp[239]{YangWei2017}}, 
\citet[269]{Fan1964} and \citet[143]{Sui2018} considered AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB to be possible, even though they both recognized that these two forms are rare.
Indeed, a few examples of AB\hyp{}\emph{yi}\hyp{}AB and AB\hyp{}\emph{le}\hyp{}\emph{yi}\hyp{}AB in Early Mandarin (12th to 20th centuries) (\ref{ex:AByiAB-lu}--\subref{ex:AByiAB-pu}) and Modern Mandarin (\ref{ex:AByiAB-rou1}--\subref{ex:ABleyiAB-ccl}) were found.

\footnotetext[17]{\textit{Yuanqu xuan: Luzhailang [Selected Yuanqu: Luzhailang]}, as cited in \citet[15]{Zhang2000}}
\footnotetext[18]{\textit{Yuan Ming juan: Piaotongshi [Yuan and Ming volume: Piaotongshi]}, 308, as cited in \citet[15]{Zhang2000}}
\footnotetext[19]{Rou, Shi. 1975. \textit{Roushi xiaoshuo xuanji [Selected novels of Roushi]}, 31. Beijing: People's Literature Publishing House.}
\footnotetext[20]{Li, Jieren. 1962. \textit{Da bo [Great wave]}, vol. 3, 171. Beijing: The Writers Publishing House.}
\ea\label{ex:ABleyiAB}
\ea\label{ex:AByiAB-lu}
\gll ni yu wo \textit{zhengli-yi-zhengli}.\footnotemark\\
you let me arrange-one-arrange\\
\glt `Let me arrange it a little bit!'

\ex\label{ex:AByiAB-pu}
\gll ni \textit{dating-yi-dating}.\footnotemark\\
you inquire-one-inquire\\
\glt `Inquire about it a little bit!'

@@

\ex\label{ex:ABleyiAB-ccl}
\gll jiduo sanluan-zhe de chuan li de dengguang, ye huyinhumie de \textit{bianhuan-le-yi-bianhuan} weizhi.\\
many scattered-\textsc{dur} \textsc{de} boat in \textsc{de} light also flicker \textsc{de} change-\textsc{pfv}-one-chang position\\ \hfill {(CCL)}
\glt `Many scattered lights in the boats also changed their positions a little bit, flickering.'
\z
\z

@@

\ea\label{ex:AyiAkan}
\ea
\gll teyi gongneng de yanjiuzhe-men bufang ruci \textit{shi-yi-shi-kan} \ldots\\
special power \textsc{de} researcher-\textsc{pl} may.as.well such try-one-try-look\\ \hfill {(CCL)}
\glt `Researchers of special power may as well have a try as such as see \ldots'

\ex 
\gll danshi dui fa mei fa-guo hege-zheng, yijing shuo bu qing le, xuyao \textit{cha-yi-cha-kan}.\\
but about issue not issue-\textsc{exp} conformity-certificate already say not clealy \textsc{ptc} need check-one-chek-look\\ \hfill {(CCL)}
\glt `But one already cannot say it clearly anymore, whether a certificate of conformity is issued or not. One needs to have a check and see.'

\ex
\gll rang wo lai \textit{cai-yi-cai-kan}.\\
let I come guess-one-guess-look\\ \hfill {({CCL})}
\glt `Let me have a guess.'

\ex
\gll da-laoban-men yao \textit{deng-yi-deng-kan}\\
big-boss-\textsc{pl} need wait-one-wait-look\\ \hfill {(CCL)}
\glt `Big bosses need to wait a little bit and see.'

\ex
\gll furen ni dao \textit{shu-yi-shu-kan}, zhe zhu hua de huaduo gong you ji zhong yanse.\\
madam you just count-one-count-look this \textsc{clf} flower \textsc{de} blossom in.total have how.many \textsc{clf} color\\ \hfill {(CCL)}
\glt `Madam, just try to count and see how many colors the blossom of this flower has in total.'
\z
\z
Due to the prominent tentative, trying meaning of AA-\textit{kan} and A-\textit{kan}-\textit{kan}, they are not compatible with the perfective aspect marker \textit{le} semantically,
as one usually cannot try something that is already realized.
Thus, structures such as  A\hyp{}\textit{le}\hyp{}A\hyp{}\textit{kan} and A\hyp{}\textit{kan\hyp{}le\hyp{}kan} are considered pragmatically infelicitous.
